Designing an effective intervention of motivational interview using sequence classification methods

### 2017-03-02 paper/AMIA/main.tex
update discussion sections
update data collection subsection

@@

Second, overall performance of hidden Markov model is better than general Markov model in both type of sequences. We observed that hidden Markov model achieved near-human accuracy to categories the sequences of behavior codes. This means that hidden states capture the propagated information passes through the sequence for determining final outcome.

>>>>

Annotation column in Table~\ref{tab:anno_examp} shows the sequence of behavior codes from top to bottom, where counselor start with an open-ended question and get positive feedback at the end. \\

@@

Second, overall performance of hidden Markov model is better than general Markov model in both type of sequences. We observed that hidden Markov model achieved near-human accuracy to categories the sequences of behavior codes. This means that hidden states capture the information passes through the codes of the utterance sequence for determining final outcome.
